---
title: "Logistic Regression Package: log.reg.11"
author: "Group 11: Charles Benfer, Ernest Asante, Rongjing Xia"
date: "11-30-2023"
output: github_document
---

### Introduction
This is an R package for performing logistic regression, implemented through numerical optimization. This package contains the basic functions needed to perform logistic regression, including estimating a vector of coefficients `β` containing independent/predictor variables and intercepts, confidence intervals for `β`, a fitted logistic curve plot of the response, and the resulting "confusion matrix" and plotting each cut_off Plot of different indicator values corresponding to the values. Also includes help documentation for all functions.

### Install the package

First, users can download the latest package through github through the following code 'devtools::install_github("R-4-Data-Science/Final-Project-Group-11")'.(If the user does not have the ‘devtools’ package installed, this package needs to be installed first)

```{r install the package, include=TRUE}
devtools::install_github("R-4-Data-Science/Final-Project-Group-11")
library(log.reg.11)
```
Next, we will borrow a set of data to show how the main functions in our package have been output and displayed.
```{r import example data set, include=TRUE}
 #data obtained from https://stats.oarc.ucla.edu/r/dae/logit-regression/
test_data <- read.csv("https://stats.idre.ucla.edu/stat/data/binary.csv")

```

### 1. Finding the Betas: `log_betas`
This function will spit out the desired beta values for the log loss function.
The function `log_loss` is first defined in the package, given as a premise a number representing a given loss.
The user will be shown a list in the output, where the first part `par` is the betas.
Y representing the column of the data that you want to be the response variable and X representing the column(s) of the data that you want to be the predictor variable(s).
```{r the example for the function log_betas, include=TRUE}

test_resp <- 1
test_pred <- 2:4
log_betas(Data = test_data, Y = test_resp, X = test_pred)
```

### 2. Bootstrap Logistic Regression Confidence Intervals: `bootstrap_logistic_confidence`
This function will help the user calculate bootstrap confidence intervals for the coefficients estimated by a logistic regression model.
Next we will continue to use the data just now to show the confidence interval calculated by our function.
```{r the example for the function bootstrap_logistic_confidence, include=TRUE}
results <- suppressWarnings(bootstrap_logistic_confidence(test_data, test_resp, test_pred))
print(results)

```

### 3. Plot of the fitted logistic curve to the responses: `logistic_plot`
This function will help the user Plot of the fitted logistic curve to the responses estimated by the logistic regression model.
The example:
```{r the example for the function logistic_plot,include=TRUE}

logistic_plot(test_data, Resp = 1, Pred= 3)

```

### 4. Confusion matrix and related indicators: `confusion_matrix`
This function help user create the confusion matrix and also output the following metrics: prevalence, accuracy, sensitivity, specificity, false discovery rate, and diagnostic odds ratio based on this cut-off value 0.5. 
This function will output a list including the values of the above indicators, in the part of the corresponding name.
The example:
```{r the example for the function confusion_matrix}
result <- confusion_matrix(Data = test_data, X=test_pred, y=test_resp, cut_off = 0.5)
print(result)

```

### 5. Plot different cut_off value versus indicators: `plot_confusion_matrix`
The possibility for the user to plot of any of the above metrics evaluated over a grid of cut-off values for prediction going from 0.1 to 0.9 with steps of 0.1.
Parameter `value_name` requires the user to specify among 6 indicators(`prevalence`, `accuracy`, `sensitivity`, `specificity`, `false_discovery_rate`, `diagnostic_odds_ratio`). If the input is incorrect, the user will be prompted in the output that "the indicator does not exist". If the user does not select an indicator, a plot of prevalence versus different cut_off values is output.
```{r the example for the function plot_confusion_matrix, include=TRUE}
plot_confusion_matrix(Data = test_data, y = test_resp,X = test_pred , value_name = 'false_discovery_rate')
# The example for not exist.
plot_confusion_matrix(Data = test_data, y = test_resp,X = test_pred , value_name = 'false_discovery')
```

### 6. For the bonus part
Our package created a shiny app that allows the used to view each of the plots by making a selection from a dropdown menu.


Framework reference link for this introduction:https://chat.openai.com/share/d590f325-5ab6-4642-98d4-127034991dbb
